### 2019-11-28 README.Rmd
tests

The **gosset** package provides an environment for modelling metadata and experimental citizen science data.

@@

**gosset** is under development. Use with caution.

@@

The full functionality of **gosset** is illustrated in the package vignette. The vignette can be found on the [package website](https://agrobioinfoservices.github.io/gosset/) or from within R once the package has been installed.

>>>>

The **gosset** package provides the toolkit for a workflow on modelling metadata and experimental citizen science data, from collating data of different sources, model sellection and visualisation. The package is named after W.S. Gosset aka 'Student', a pioneer of modern statistics in small sample experimental design and analysis.

@@

@@

The full functionality of **gosset** is illustrated in the package vignette. The vignette can be found on the [package website](https://agrobioinfoservices.github.io/gosset/).
